---
title: "Affan's WebJournal"
author: "Muhammad Affan Qamar"
date: "09-May-2022"
output:
 html_document:
    theme: cosmo
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 4
    #code_folding: hide

---

```{css, echo=FALSE}
body {
  color: black;
  background-color: #cde5e6;
  background-position: center top;
    background-size: cover;
    background-repeat: no-repeat;
  font-family:'Open Sans',sans-serif;
}
.list-group-item, .list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
  color: black;
  background-color: #a0f26d;
  border-color: #black;
  border-width: 6px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=TRUE,
  message=FALSE,
  warning=FALSE,
  cache=TRUE
  )
```

Last compiled: `r Sys.Date()`

# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----
## Challenge Summary 
1. Analyze the sales by location (state) with a bar plot. Since state and city are multiple features (variables), they should be split. Which state has the highest revenue? Replace your bike_orderlines_wrangled object with the newly wrangled object (with the columns state and city).

2.Analyze the sales by location and year (facet_wrap). Because there are states with bike stores, you should get 12 plots.

# 1.0 Load libraries ----

```{r t1p0, fig.height=7, fig.width=10, message=FALSE}
library(tidyverse)
library(jsonlite)
library(xml2)
library(readxl)
library(httr)
library(rvest)
library(tidyquant)
library(broom)
library(umap)
library(DT)
library(ggrepel)
library(lubridate)
library(wesanderson)
library(ggplot2)

```


# 2.0 Importing Files ----

```{r}

bikes_tbl <- read_excel(path = "C:/Users/Muhammad Affan Qamar/Documents/GitHub/bdsc-affan1947/00_data/01_bike_sales/01_raw_data/bikes.xlsx")

orderlines_tbl <- read_excel(path = "C:/Users/Muhammad Affan Qamar/Documents/GitHub/bdsc-affan1947/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")

bikeshops_tbl  <- read_excel(path = "C:/Users/Muhammad Affan Qamar/Documents/GitHub/bdsc-affan1947/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx" )

```
# 3.0 Examining Data ----

```{r}
orderlines_tbl
bikes_tbl

```

# 4.0 Joining Data ----

If the data has no common column name, you can provide each column name in the "by" argument. For example, by = c("a" = "b") will match x.a to y.b. The order of the columns has to match the order of the tibbles).

```{r}
bike_orderlines_joined <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

```

# 5.0 Wrangling Data ----

```{r}
bike_orderlines_wrangled <- bike_orderlines_joined %>%
                             # Split up location data for Part 1
                            separate(col    = location,
                                     into   = c("city", "state"),
                                     sep    = ", ") %>%
                            # Split up date data for Part 2
                            separate(col = order.date, 
                                     into = c("year", "month", "day"),
                                     sep = "-") %>%
                            # Calculate and add total price data
                            mutate(total.price = price * quantity)

```

# 6.0 Business Insights ----


## Part 1: Analyze the Sales by location(state)
Analyze the sales by location (state) with a bar plot. Since state and city are multiple features (variables), they should be split. Which state has the highest revenue? Replace your bike_orderlines_wrangled object with the newly wrangled object (with the columns state and city).

```{r plot, fig.width=10, fig.height=7, message=FALSE}
#Create frame with price data by State

sales_by_state <- bike_orderlines_wrangled %>%
  # Select relevant data (state and total price)
  select(state,total.price) %>%
  # Sum all the prices for each state
  group_by(state) %>%
  summarize(sales=sum(total.price)) %>%
  # draw labels for bar graph
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

# making it presentable

sales_by_state %>% ggplot(aes(x=state, y=sales)) +
  geom_col(fill = wes_palette("Darjeeling1", 4)[4]) +
                  geom_label(aes(label = sales_text)) + 
                  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", suffix = " €")) +
                  labs(
                       title = "Lifetime Sales",
                       subtitle = "Overview of lifetime sales in German states") +
                  xlab("German State") + ylab("Lifetime Sales") +
                  theme(axis.text.x = element_text(angle = 47, hjust = 1))

```


# Part 2:The sales by location and year 
Analyze the sales by location and year (facet_wrap). Because there are 12 states with bike stores, you should get 12 plots.

```{r t1p2, fig.height=7, fig.width=10, message=FALSE}
# Create frame with price data by states and by year
sales_by_state_by_year <- bike_orderlines_wrangled %>% 
                        # Select relevant data (state, year, total price)
                        select(year, state, total.price) %>%
                        # Group by year and sum the order totals for each state
                        group_by(year, state) %>%
                        summarize(sales=sum(total.price)) %>%
                        # Making it presentable
                        mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                   decimal.mark = ",", 
                                   prefix = "", 
                                   suffix = " €"))

sales_by_state_by_year %>%  ggplot(aes(x = year, y = sales, fill = state)) +
  geom_col() +
  facet_wrap(~ state) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                                              suffix = " €")) +
  labs(
    title = "Revenue by year",
    subtitle = "Revenue in each State by year") +
  scale_fill_manual(values = wes_palette("Darjeeling1", 13,
                                         type = "continuous")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 47, hjust = 1))

```

Done !!
