---
title: "02 Data Acqusition"
author: "Muhammad Affan Qamar"
date: "2021-05-10"
output:
 html_document:
    theme: cosmo
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 4
    #code_folding: hide
---

```{css, echo=FALSE}
body {
  color: black;
  background-color: #cde5e6;
  background-position: center top;
    background-size: cover;
    background-repeat: no-repeat;
  font-family:'Open Sans',sans-serif;
}
.list-group-item, .list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
  color: black;
  background-color: #a0f26d;
  border-color: #black;
  border-width: 6px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

Last compiled: `r Sys.Date()`

# Data Science at TUHH ------------------------------------------------------

# Data Acquisition Challenges

### Import Libraries
```{r t2p1, fig.height=7, fig.width=10, message=FALSE}
library(dplyr)
library(tidyverse)
library(rvest)
library(xopen)
library(jsonlite)
library(glue)
library(wesanderson)
library(RSQLite)
library(stringi)
library(DBI)
library(httr)
library(kableExtra)
```

# Part 1 Data via API
## Checking the weather forecast for Hamburg using Accuweather API

### key
key can be requested by making a new account at https://developer.accuweather.com/ 
note: it can only be used to request API 50 times in one day.

```{r}
KEY <- "qudWjbI6ZckdGo3PuJ9jA6Satip51yly"
```

## Build URL and call API
```{r}
raw_accuweather_data <- GET(glue("http://dataservice.accuweather.com/forecasts/v1/daily/1day/178556?apikey={KEY}"))

#use of content function

my_content <- httr::content(raw_accuweather_data, as = 'text')

```
## From text to more useable R object
```{r}

my_content_json <- jsonlite::fromJSON(my_content)
# run dplyr glimpse to get a good look at the structure
dplyr::glimpse(my_content_json)
```
## Making the forecast in more organized way
```{r}
forecast_df <- my_content_json$DailyForecasts
dplyr::glimpse(forecast_df)
```
## Maling it nice looking
```{r, results='asis'}
forecast_df %>%
  knitr::kable(caption = "Hamburg Daily Forecast AccuWeather",) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

# Part 2 Scrape and create a data base
Scrape one of the competitor websites of canyon (either https://www.rosebikes.de/ or https://www.radon-bikes.de) and create a small database. The database should contain the model names and prices for at least one category.
After scraping your data, convert it to a readable format. Prices should be in a numeric format without any other letters or symbols. Also check if the prices are reasonable.

```{r}
base_url <- 'https://www.rosebikes.com/bikes'

# 1. Function to get bike family URLs.
get_bike_family_urls <- function(base_url) {
  
  bike_family_urls <- read_html(base_url) %>%
    html_nodes(css = ".catalog-categories-item > a") %>%
    html_attr('href') %>%
    
    # Convert vector to tibble
    
    enframe(name = "position", value = "subdirectory") %>%
    # Add the domain because we will get only the subdirectories
    mutate(
      url = glue('https://www.rosebikes.com{subdirectory}')
    ) 
  
  bike_family_urls <- bike_family_urls %>% 
    filter(!grepl('sale', url)) %>%
    filter(!grepl('kids', url))
  bike_family_urls <- bike_family_urls['url']
  
}


# 2. Function to get bike family URLs.

get_model_urls <- function(url) {
  
  bike_type_url <- read_html(url) %>%
    html_nodes(css = ".catalog-category-bikes__content > a") %>%
    html_attr('href') %>%
    enframe(name = "position", value = "url") %>%
    mutate(url = glue('https://www.rosebikes.com{url}')) 
}


# 3. Function to get the names of each bike 

get_bike_names <- function(url) {
  
  bike_model_name_tbl <- read_html(url) %>%
    html_nodes(css = ".catalog-category-model__title") %>%
    html_text() %>%
    # Convert vector to tibble
    as_tibble()
    
  
}

# 4. Function to get the prices of each bike 

get_bike_prices <- function(url) {
  
  bike_model_price_tbl <- read_html(url) %>%
    html_nodes(css = ".product-tile-price__current-value") %>%
    html_text() %>%
    # Convert vector to tibble
    as_tibble()
  
}



#### APPLYING ABOVE FUNCTIONS

bike_family_url_tbl <- get_bike_family_urls(base_url)
bike_family_url_tbl <- bike_family_url_tbl %>%
  slice(1:3) # Pick 3 categories




# Create a table with bike model URLS
bike_model_url_tbl <- tibble()

for (i in seq_along(bike_family_url_tbl$url)) {
  
  web <- toString(bike_family_url_tbl$url[i])
  bike_model_url_tbl <- bind_rows(bike_model_url_tbl, get_model_urls(web))
  
}


# Create a table with bike model names
bike_model_names_tbl <- tibble()

for (i in seq_along(bike_model_url_tbl$url)) {
  
  web <- toString(bike_model_url_tbl$url[i])
  bike_model_names_tbl <- bind_rows(bike_model_names_tbl, get_bike_names(web))
  
}

# Rename cols
names(bike_model_names_tbl)[1] <- "Bike Model"



# Create a table with bike prices
bike_model_prices_tbl <- tibble()

for (i in seq_along(bike_model_url_tbl$url)) {

  web <- toString(bike_model_url_tbl$url[i])
  bike_model_prices_tbl <- bind_rows(bike_model_prices_tbl, get_bike_prices(web))

}

# Rename cols
names(bike_model_prices_tbl)[1] <- "Bike Prices"
```

```{r}
# Join into one table
table_of_prices <- bind_cols(bike_model_names_tbl,bike_model_prices_tbl)

```

```{r, results='asis'} 
knitr::kable(table_of_prices[1:10, ], caption = 'Rosebike Bike Model & Prices') %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

Done !!